---
title: "Basics of R and RStudio, Part II"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```

## Lecture Video

The following video was produced by R-Ladies Sydney as part of their online textbook [RYouWithMe](https://rladiessydney.org/courses/ryouwithme/).

<iframe width="560" height="315" src="https://www.youtube.com/embed/v6VygIgvoZU" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

## Econometrics Packages

We will use many packages in this class, so now would be a good time to install them. Specifically, we will use the following packages:

1. `tidyverse` The tidyverse is a collection of commonly used packages designed around a set of programming principles ("tidy data"). We will not emphasize these principles in this class, but knowledge of the tidyverse is becoming an increasingly valuable skill set in the labor market. The book [R for Data Science](https://r4ds.had.co.nz/) is a an excellent introduction to the tidyverse, if you are interested in learning more. *Note: Some of you may have difficulty installing the tidyverse on your personal computer. Skip it for now if you are having any trouble.*
2. `wooldridge` This package contains most of the datasets that we will use in this class.
3. `lfe` We will use this package to run regressions.
4. `car` Another package that will help us with regressions.
5. `stargazer` A package that allows us to visualize regression output.

Install these packages from the "Packages" tab in RStudio, or by typing the following into the RStudio Console:

```{r, eval=F}
install.packages("tidyverse")
install.packages("wooldridge")
install.packages("lfe")
install.packages("car")
install.packages("stargazer")
```



[Previous](1_2.html) | [Table of contents](1_0.html) | [Next](1_4.html) 
