---
title: "Stats Review: Confidence Intervals"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```

## Lecture Video

<iframe width="560" height="315" src="https://www.youtube.com/embed/hV4pdjHCKuA" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

[Click here to view the video on the Khan Academy website.](https://www.khanacademy.org/math/statistics-probability/confidence-intervals-one-sample/old-confidence-interval-videos/v/t-statistic-confidence-interval)

## R Example

Continue using the previous data:

```{r, eval=T}
x <- c(15.6, 16.2, 22.5, 20.5, 16.4, 19.4, 16.6, 17.9, 12.7, 13.9)
```

First we find the critical t-values for the two-sided test at the 95% confidence level. But since R does not have the ability to calculate two-sided tests, we can use the fact that a t-distribution is symmetric to find the one-sided critical values associated with a 97.5% confidence level (1 - 0.05/2). 

```{r, eval=T}
n <- length(x)
tcrit <- qt(0.975, n-1)
```

Now we can calculate the upper and lower bounds on our 95% confidence interval:

```{r, eval=T}
xbar <- mean(x)
sdx <- sd(x)

upperci <- tcrit*(sdx/sqrt(n)) + xbar
lowerci <- -tcrit*(sdx/sqrt(n)) + xbar

c(lowerci, upperci)
```


## Practice Question
Calculate a 99% confidence interval for $\mu$. 

<div id="spoiler" style="display:none">

```{r, eval=T}
tcrit <- qt(0.995, n-1)

upperci <- tcrit*(sdx/sqrt(n)) + xbar
lowerci <- -tcrit*(sdx/sqrt(n)) + xbar

c(lowerci, upperci)
```


</div>

<button title="Click to Show/Hide Content" type="button" onclick="if(document.getElementById('spoiler') .style.display=='none') {document.getElementById('spoiler') .style.display=''}else{document.getElementById('spoiler') .style.display='none'}">Show/Hide Solution</button>



[Previous](1_5.html) | [Table of contents](1_0.html) 
