---
title: "Homoscedasticity"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)

library(wooldridge)
library(ggplot2)
data(wage2)

```

## Lecture Video

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/391241/sp/39124100/embedIframeJs/uiconf_id/22119142/partner_id/391241?iframeembed=true&playerId=kaltura_player&entry_id=0_o20rc9r4&flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[hotspots.plugin]=1&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=0_7r7wibya" width="720" height="480"  allow="autoplay *; fullscreen *; encrypted-media *" sandbox="allow-forms allow-same-origin allow-scripts allow-top-navigation allow-pointer-lock allow-popups allow-modals allow-orientation-lock allow-popups-to-escape-sandbox allow-presentation allow-top-navigation-by-user-activation" frameborder="0" title="Kaltura Player"></iframe>


## Practice Question
Consider the following two models:

$$wage = \beta_0 + \beta_1 educ + u ~~~~~~~~ (1)$$

$$\ln(wage) = \beta_0 + \beta_1 educ + u ~~~~~~ (2)$$

Using the data from the `wage2` dataset, for which model does it appear that SLR5 is most likely to hold?

<div id="spoiler" style="display:none">

Let's begin by plotting the data for model (1):

```{r}
qplot(y=wage, x=educ, data=wage2) +
    geom_smooth(method="lm")
```

Note that we are "adding" the `geom_smooth()` function to our plot. This function adds an OLS line if we pass the "lm" argument to the function. From the plot, we see that the variance of wages given education seems to vary considerably by education level. Specifically, individuals in the sample with low education (9, 10, 11 years) have low variance in wages. By comparison, individuals with high education (16, 17, 18 years) have a wide dispersion in wages. It therefore appears that the variance of $\widehat{u}$ depends on education, which is a violation of SLR5.

Now consider model (2):

```{r}
qplot(y=lwage, x=educ, data=wage2) +
    geom_smooth(method="lm")
```

In comparison to model (1), the variance of $\widehat{u}$ appears to be more uniform across education. While wages appear to be somewhat less varying at low levels of education than at high levels, the pattern is much less pronounced in model (2) than in model (1). It therefore appears that SLR5 is more likely to hold true in model (2).

</div>

<button title="Click to Show/Hide Content" type="button" onclick="if(document.getElementById('spoiler') .style.display=='none') {document.getElementById('spoiler') .style.display=''}else{document.getElementById('spoiler') .style.display='none'}">Show/Hide Solution</button>


[Back](2_10.html) | [Table of contents](2_0.html) | [Next](2_12.html) 
