---
title: "Standard Errors"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)

library(wooldridge)
library(ggplot2)
data(wage2)
```

## Lecture Video

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/391241/sp/39124100/embedIframeJs/uiconf_id/22119142/partner_id/391241?iframeembed=true&playerId=kaltura_player&entry_id=0_fkoy2smg&flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[hotspots.plugin]=1&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=0_7r7wibya" width="720" height="480"  allow="autoplay *; fullscreen *; encrypted-media *" sandbox="allow-forms allow-same-origin allow-scripts allow-top-navigation allow-pointer-lock allow-popups allow-modals allow-orientation-lock allow-popups-to-escape-sandbox allow-presentation allow-top-navigation-by-user-activation" frameborder="0" title="Kaltura Player"></iframe>


## Standard Error Estimation in R

We've seen theoretically how to calculate the standard errors of the OLS estimate $\widehat{\beta}_1$. Luckily, R does most of the hard work for us when we want to calculate standard errors using real-world data. In fact, we've already seen them!

```{r, eval=T}
wage_reg <- lm(wage ~ educ, data=wage2)
summary(wage_reg)
```

R reports the standard errors for the OLS estimates in the `Std. Error` column from the summary results. From the results, we see that $se(\widehat{\beta}_1) = 5.695$.

## Practice Question

Suppose we restrict our sample to people who have less than a college degree (education less than 16 years). What do we expect to happen to the standard error of $\widehat{\beta}_1$?

<div id="spoiler" style="display:none">

As we restrict the sample, SST\textsubscript{X}, the variance in education, will decrease. We therefore expect the standard error to increase. 

We can test this directly in R by using the `subset()` function to create a new data frame:

```{r}
wage2_nocollege <- subset(wage2, educ < 16)
nocollege_reg <- lm(wage ~ educ, data=wage2_nocollege)
summary(nocollege_reg)
```

The standard error has increased to $se(\widehat{\beta}_1) = 11.44$


</div>

<button title="Click to Show/Hide Content" type="button" onclick="if(document.getElementById('spoiler') .style.display=='none') {document.getElementById('spoiler') .style.display=''}else{document.getElementById('spoiler') .style.display='none'}">Show/Hide Solution</button>


[Back](2_11.html) | [Table of contents](2_0.html) 
