---
title: "Goodness of Fit"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)

library(wooldridge)
library(ggplot2)
data(wage2)
wage_reg <- lm(wage ~ educ, data=wage2)
```

## Lecture Video

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/391241/sp/39124100/embedIframeJs/uiconf_id/22119142/partner_id/391241?iframeembed=true&playerId=kaltura_player&entry_id=0_cwtbgmuo&flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[hotspots.plugin]=1&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=0_7r7wibya" width="720" height="480"  allow="autoplay *; fullscreen *; encrypted-media *" sandbox="allow-forms allow-same-origin allow-scripts allow-top-navigation allow-pointer-lock allow-popups allow-modals allow-orientation-lock allow-popups-to-escape-sandbox allow-presentation allow-top-navigation-by-user-activation" frameborder="0" title="Kaltura Player"></iframe>


## Summarizing a Regression in R

As we saw in the last section, the output of the `lm()` function is an object that contains a lot of valuable information. We can quickly view some of the most important pieces of information from our regression by using the `summary()` command on the regression object:

```{r, eval=T}
summary(wage_reg)
```

Specifically, R automatically calculates the $R^2$ of the regression and reports it as:

```
Multiple R-squared:  0.107
```

In this sample, 10.7% of the variation in wages is explained by the variation in education.


## Practice Question
Calculate the $R^2$ for the regression model:

$$\ln(wage) = \beta_0 + \beta_1 educ + u$$


<div id="spoiler" style="display:none">

```{r, eval=T}
log_wage_reg <- lm(lwage ~ educ, data=wage2)
summary(log_wage_reg)

## Calculate directly with:
## summary(log_wage_reg)$r.squared
```

</div>

<button title="Click to Show/Hide Content" type="button" onclick="if(document.getElementById('spoiler') .style.display=='none') {document.getElementById('spoiler') .style.display=''}else{document.getElementById('spoiler') .style.display='none'}">Show/Hide Solution</button>



[Back](2_4.html) | [Table of contents](2_0.html) | [Next](2_6.html) 
