---
title: "Coefficient Interpretation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)

library(wooldridge)
library(ggplot2)
data(wage2)
```

## Lecture Video

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/391241/sp/39124100/embedIframeJs/uiconf_id/22119142/partner_id/391241?iframeembed=true&playerId=kaltura_player&entry_id=0_0fzbr8q9&flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[hotspots.plugin]=1&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=0_7r7wibya" width="720" height="480"  allow="autoplay *; fullscreen *; encrypted-media *" sandbox="allow-forms allow-same-origin allow-scripts allow-top-navigation allow-pointer-lock allow-popups allow-modals allow-orientation-lock allow-popups-to-escape-sandbox allow-presentation allow-top-navigation-by-user-activation" frameborder="0" title="Kaltura Player"></iframe>


## Log-Log Regressions in R

Suppose we wish to estimate the log-log model:

$$\ln(wage) = \beta_0 + \beta_1 \ln(educ) + u$$

In the `wage2` dataset, we have a variable that corresponds to $\ln(wage)$, called `lwage`. However, we don't have a variable for $\ln(educ)$. Let's add one to the data frame:

```{r}
wage2$leduc <- log(wage2$educ)
```

A new variable is added to the `wage2` data frame, called `leduc`. It is the natural log of the `educ` variable from the same data frame.

Now we can run the log-log regression:

```{r}
lm(lwage ~ leduc, data=wage2)
```




[Back](2_5.html) | [Table of contents](2_0.html) | [Next](2_7.html) 
