---
title: "OLS Derivation, Part I"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
source(week3.R)
```

## Lecture Video

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/391241/sp/39124100/embedIframeJs/uiconf_id/22119142/partner_id/391241?iframeembed=true&playerId=kaltura_player&entry_id=0_d28958g8&flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[hotspots.plugin]=1&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=0_m48krxrh" width="720" height="480"  allow="autoplay *; fullscreen *; encrypted-media *" sandbox="allow-forms allow-same-origin allow-scripts allow-top-navigation allow-pointer-lock allow-popups allow-modals allow-orientation-lock allow-popups-to-escape-sandbox allow-presentation allow-top-navigation-by-user-activation" frameborder="0" title="Kaltura Player"></iframe>


## R Example

Recall the simple linear regression of education on wages:

$$wage = \beta_0 + \beta_1 educ + u$$

As discussed in the video above, we might be concerned that assumption SLR4 doesn't hold because some of our unexplained factors in $u$ may be related to both education and wages. Specifically, we might think that we should include experience as an explanatory variable:

$$wage = \beta_0 + \beta_1 educ + \beta_2 exper + u$$

Luckily, the `wage2` dataset includes an experience variable, called `exper`. Estimating the multiple regression model is as simple as adding this variable to our `lm()` call:

```{r, eval = T}
mlr <- lm(wage ~ educ + exper, data=wage2)
summary(mlr)
```

We now have estimates of $\widehat{\beta_0}$, $\widehat{\beta_1}$, and $\widehat{\beta_2}$. R reports these estimates in the "Estimate" column in the summary output, where `(Intercept)` corresponds to $\widehat{\beta_0}$, `educ` refers to $\widehat{\beta_1}$, and `exper` refers to $\widehat{\beta_2}$. 

## Practice Question

Estimate the model:

$$wage = \beta_0 + \beta_1 educ + \beta_2 exper + \beta_3 age + u$$

<div id="spoiler" style="display:none">
```{r}
mlr2 <- lm(wage ~ educ + exper + age, data=wage2)
summary(mlr2)
```{r}
</div>

<button title="Click to Show/Hide Content" type="button" onclick="if(document.getElementById('spoiler') .style.display=='none') {document.getElementById('spoiler') .style.display=''}else{document.getElementById('spoiler') .style.display='none'}">Show/Hide Solution</button>


[Table of contents](3_0.html) | [Next](3_2.html)
