---
title: "Omitted Variables"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
source(week3.R)
```

## Lecture Video

<iframe id="kaltura_player" src="https://cdnapisec.kaltura.com/p/391241/sp/39124100/embedIframeJs/uiconf_id/22119142/partner_id/391241?iframeembed=true&playerId=kaltura_player&entry_id=0_d28958g8&flashvars[localizationCode]=en&amp;flashvars[leadWithHTML5]=true&amp;flashvars[sideBarContainer.plugin]=true&amp;flashvars[sideBarContainer.position]=left&amp;flashvars[sideBarContainer.clickToClose]=true&amp;flashvars[chapters.plugin]=true&amp;flashvars[chapters.layout]=vertical&amp;flashvars[chapters.thumbnailRotator]=false&amp;flashvars[streamSelector.plugin]=true&amp;flashvars[EmbedPlayer.SpinnerTarget]=videoHolder&amp;flashvars[dualScreen.plugin]=true&amp;flashvars[hotspots.plugin]=1&amp;flashvars[Kaltura.addCrossoriginToIframe]=true&amp;&wid=0_zgkm9vzl" width="720" height="480"  allow="autoplay *; fullscreen *; encrypted-media *" sandbox="allow-forms allow-same-origin allow-scripts allow-top-navigation allow-pointer-lock allow-popups allow-modals allow-orientation-lock allow-popups-to-escape-sandbox allow-presentation allow-top-navigation-by-user-activation" frameborder="0" title="Kaltura Player"></iframe>


## R Example

Return to the simple linear regression and the multiple linear regression models:

$$\tilde{wage} = \tilde{\beta}_0 + \tilde{\beta}_1 educ$$
$$\widehat{wage} = \widehat{\beta}_0 + \widehat{\beta}_1 educ + \widehat{\beta}_2 exper$$
$$\widehat{exper} = \widehat{\delta}_0 + \widehat{\delta}_1 educ$$

In R, we can estimate the size of the omitted variable bias that is caused by the omission of the experience variable by simply multiplying $\widehat{\beta}_2$ by $\widehat{\delta}_1$:

```{r, eval=T}
beta2hat*delta1hat
```

According to the calculation, the simple linear regression appears to *underestimate* $\beta_1$ when we omit experience as an explanatory variable.

## Practice Question

We can't observe ability directly. However, the `wage2` dataset has a variable that records people's score on an IQ exam, which is likely correlated with ability. If we include the IQ variable in the multiple regression model, what would we expect to happen to the estimate of $\beta_1$, the coefficient on education?

<div id="spoiler" style="display:none">
We expect people with higher IQ scores to have higher income on average ($beta_2 > 0$), and we also expect people with high IQ scores to stay in school for a longer period of time ($\delta_1 > 0$). The ability omitted variable is therefore likely biasing our estimates upward, and by including IQ in our regression we would expect the estimate of $\beta_1$ to decrease.
</div>

<button title="Click to Show/Hide Content" type="button" onclick="if(document.getElementById('spoiler') .style.display=='none') {document.getElementById('spoiler') .style.display=''}else{document.getElementById('spoiler') .style.display='none'}">Show/Hide Solution</button>


[Previous](3_7.html) | [Table of contents](3_0.html) | [Next](3_9.html)
