---
title: "Goodness of Fit: Adjusted R-squared, Part I"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=T)
```

## Lecture Video

**Embedded video:**[https://media.oregonstate.edu/media/t/0_ca5pxl9w](https://media.oregonstate.edu/media/t/0_ca5pxl9w)

## R Example
Open the `week5.R` script that we started previously and click the "Source" button to execute all of the commands. 

One advantage of $\bar{R}^2$ is that it can be particularly useful in comparing non-nested models. A nested model is one that can be written as a special case of another model.  An example of a non-nested model would be if we wrote:

$$rdintens = \beta_0 + \beta_1 \ln(sales) + u$$
$$rdintens = \beta_0 + \beta_1 sales + \beta_2 sales^2 + u$$

```{r, echo=F}
data(rdchem)
lm_log <- lm(rdintens ~ lsales, data=rdchem)
lm_quad <- lm(rdintens ~ sales + salessq, data=rdchem)
```

Compare the regression results:

```{r}
summary(lm_log)
```

```{r}
summary(lm_quad)
```

In this case the models are non-nested because they aren’t special cases of each other. We therefore can’t refer to one as the unrestricted model and the other as the restricted model, and we also therefore can’t run an F test to choose between them. 

Instead, $\bar{R}^2$ can help: we could look at the $\bar{R}^2$ of the two models and choose the one that is higher. Of course, we could also use $R^2$ for this purpose, but why might $\bar{R}^2$ be more
useful in this case? Because $\bar{R}^2$ will penalize the second model for having more explanatory
variables.

When we compare the regression output, the adjusted $R^2$ ($\bar{R}^2$) is higher in the second model (the quadratic specification). We should therefore prefer that model.


## Practice Question
Compare the above two specifications to a simple linear specification:

$$rdintens = \beta_0 + \beta_1 sales + u$$

Is this model better or worse than the other two?

<div id="spoiler" style="display:none">

```{r}
lm_lin <- lm(rdintens ~ sales, data=rdchem)
summary(lm_lin)
```

The adjusted $R^2$ is 0.015, lower than the other two models. We should avoid the linear specification.

</div>

<button title="Click to Show/Hide Content" type="button" onclick="if(document.getElementById('spoiler') .style.display=='none') {document.getElementById('spoiler') .style.display=''}else{document.getElementById('spoiler') .style.display='none'}">Show/Hide Solution</button>



---

[Previous](r2.html) | [Table of contents](toc.html) | [Next](ar2_II.html) 
