---
title: "Data Scaling, Part II"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```

## Lecture Video
**Embedded video:** [https://media.oregonstate.edu/media/t/0_7lxbkdlz](https://media.oregonstate.edu/media/t/0_7lxbkdlz)

## R Example
Open the `week5.R` script that we started previously and click the "Source" button to execute all of the commands. 

Consider again the regression `lm1`:

$$\widehat{bwght} = \widehat{\beta}_0 + \widehat{\beta}_1 cigs + \widehat{\beta}_2 faminc$$

What if we wanted to measure cigs in terms of packs per day, not cigarettes per day? Let’s return birth weight to its original form in ounces, and measure cigarettes in packs by dividing it by 20. We’ll also multiply its coefficient by 20 so as not to change the units of any of the other variables:

$$\widehat{bwght} = \widehat{\beta}_0 + (20 \cdot \widehat{\beta}_1)(cigs/20) + \widehat{\beta}_2 faminc$$
$$\widehat{bwght} = \widehat{\beta}_0 + (20 \cdot \widehat{\beta}_1)packs + \widehat{\beta}_2 faminc$$

```{r, eval=T}
bwght$packs <- bwght$cigs/20
lm_packs <- lm(bwght ~ packs + faminc, data=bwght)
summary(lm_packs)
```

We therefore have a new independent variable called packs and we should get a coefficient that is 20 times the original coefficient on cigs. Looking at the regression output, this is exactly what we see: $-0.4634(20)=-9.268$. This matches our original prediction that a pregnant woman who smokes an additional pack per day has a baby weighing 9.27 ounces less. Note that the coefficient on $faminc$ is the same as the original regression (`lm1`), and $R^2$ is also the same. You can also see that the t-statistics are equivalent.

What we see, then, is that this kind of linear data rescaling does not fundamentally alter our results, it just changes the units in which we interpret those results. Data rescaling can be useful to place data in more natural forms of measurement, and we needn’t worry that we lose any information or get different results in the process.


## Practice Question
In some countries it is common to see half-packs containing 10 cigarettes (instead of the usual 20). How much does an additional half-pack of cigarettes per day affect birth weight *in kilograms*?

<div id="spoiler" style="display:none">

```{r, eval=T}
bwght$bwghtkg <- bwght$bwghtlbs/2.2
bwght$cigshalfpack <- bwght$cigs/10
lm_half <- lm(bwghtkg ~ cigshalfpack + faminc, data=bwght)
summary(lm_half)
```

One additional half pack of cigarettes reduces birth weight by `r abs(round(coefficients(lm_half)["cigshalfpack"], 3))` kilograms.

</div>

<button title="Click to Show/Hide Content" type="button" onclick="if(document.getElementById('spoiler') .style.display=='none') {document.getElementById('spoiler') .style.display=''}else{document.getElementById('spoiler') .style.display='none'}">Show/Hide Solution</button>



---

[Previous](data_scaling_I.html) | [Table of contents](toc.html) | [Next](quadratics_I.html) 
